Seminar 4
============================

Part 1 Following the example code:
_____________________________________
```{r}
library(lattice)
prDat  <- read.table("GSE4051_data.tsv")
str(prDat, max.level = 0)
prDes  <- readRDS("GSE4051_design.rds")
str(prDes)
set.seed(987)
(theGene  <- sample(1:nrow(prDat), 1 ))
pDat  <- data.frame(prDes, gExp = unlist(prDat[theGene, ]))
str(pDat)
aggregate(gExp ~ gType, pDat, FUN =mean)
stripplot(gType ~ gExp, pDat)
t.test(gExp ~ gType, pDat)
ttRes  <- t.test(gExp ~ gType, pDat)
str(ttRes)
ttRes$statistic
ttRes$p.value
```

To change the gene of interest I am not sure how to do that... but buy changing the seed you can get different data:
______________________________________

````{r}
set.seed(102)
(theGene <- sample(1:nrow(prDat), 1))
pDat  <- data.frame(prDes, gExp = unlist (prDat[theGene, ]))
str(pDat)
aggregate(gExp ~ gType, pDat, FUN =mean)
stripplot(gType ~ gExp, pDat)
````

```{r}
set.seed(1)
(theGene <- sample(1:nrow(prDat), 1))
pDat  <- data.frame(prDes, gExp = unlist (prDat[theGene, ]))
str(pDat)
aggregate(gExp ~ gType, pDat, FUN =mean)
stripplot(gType ~ gExp, pDat)
```
Overall, changing the seed number changes the scatter plots entirely, and I think you need to make a new design matrix to name the gene correctly otherwise you get wt/NrlKO each time. How do you make another design matrix?